Federated Learning's Blessing:\\ FedAvg has Linear Speedup

### 2020-06-03 source/sec_problem.tex
Update sec_problem.tex
minor update problem setup

Since federated learning usually involves an enormous amount of 
local devices, it is more realistic to consider only a subset of 
local devices is active at each communication round (system heterogeneity). In this work,
we consider both the case of \textbf{full participation} where the model is
averaging over all devices at the communication round, i.e.,
$\mathbf{w}_{t+1}^{k} = \sum_{k=1}^N p_k \mathbf{v}_{t+1}^{k}$, and
the case of \textbf{partial participation} where $|\cS_{t+1}| < N$. 
In the partial participation scenario, $\cS_{t+1}$ is obtained by two types
sampling schemes to simulate practical scenarios~\cite{li2019convergence}. 
The sampling scheme I establishes $\cS_{t+1}$ by i.i.d. sampling the devices according to
the weight $p_k$ with replacement. 
The sampling scheme II establishes $\cS_{t+1}$ by uniformly sampling all devices without
replacement. Both of the sampling schemes
guarantee that gradient updates in FedAvg are unbiased stochastic versions of
updates in FedAvg with full participation. For 
more details on the notations and setup, please also refer to the Section~\ref{sec:app:notations} in the appendix.

@@

\subsection{Assumptions}

We make the following standard assumptions on the objective function $F_1,\dots, F_N$. Assumption~\ref{ass:lsmooth} and Assumption~\ref{ass:stroncvx} are common assumptions satisfied by a range of popular objective functions, such as $\ell^{2}$ regularized logistic regression and cross-entropy loss functions.

>>>>

Since federated learning usually involves an enormous amount of 
local devices, it is more realistic to consider only a subset of 
local devices is active at each communication round (system heterogeneity). In this work,
we consider both the case of \textbf{full participation} where the model is
averaging over all devices at the communication round, i.e.,
$\mathbf{w}_{t+1}^{k} = \sum_{k=1}^N p_k \mathbf{v}_{t+1}^{k}$, and
the case of \textbf{partial participation} where $|\cS_{t+1}| < N$. 
In the partial participation scenario, $\cS_{t+1}$ is obtained by two types
sampling schemes to simulate practical scenarios~\cite{li2019convergence}. 
The sampling scheme I establishes $\cS_{t+1}$ by i.i.d. sampling the devices according to
the weight $p_k$ with replacement. 
The sampling scheme II establishes $\cS_{t+1}$ by uniformly sampling all devices without
replacement. Both of the sampling schemes
guarantee that gradient updates in FedAvg are unbiased stochastic versions of
updates in FedAvg with full participation. For 
more details on the notations and setup, please refer to Section~\ref{sec:app:notations} in the appendix.

@@

\subsection{Assumptions}
\label{sec:assumptions}
We make the following standard assumptions on the objective function $F_1,\dots, F_N$. Assumption~\ref{ass:lsmooth} and Assumption~\ref{ass:stroncvx} are common assumptions satisfied by a range of popular objective functions, such as $\ell^{2}$ regularized logistic regression and cross-entropy loss functions.
